%-------------------------
% Resume in Latex
% Author : Anurag Agarwal
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Anurag Agarwal} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:15146234643}{+1 514 623 4643}
    $|$
    \faAt \hspace{.5pt} \href{mailto:anuragagarwal6895@gmail.com}{anuragagarwal6895@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/anurag-agarwal6895}{anurag-agarwal}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/anuragagarwal6895}{anurag-agarwal6895}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://goo.gl/maps/wWnsUaomDb2oCBts5}{Montreal, Canada}
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Concordia University
      % \normalfont{(Admission rate: 0.09\%)}
      }{Montreal, Canada}
      {Master's of Applied Computer Science;   \textbf{}}{Sep 2022 \textbf{--} Present}
    \resumeSubheading
      {Kalinga Institute of Industrial Technology (KIIT)
      }{Bhubaneswar, India}
      {Bachelor's in Computer Science and Engineering;   \textbf{GPA: 8.39/10.0}}{Jul 2014 \textbf{--} Apr 2018}
    
  \resumeSubHeadingListEnd



%----------- WORK EXPERIENCE -----------

\section{Work Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Deloitte}{Hyderabad, India}
      {Consultant, Client: \textbf{PayPal}}{May 2022 \textbf{--} August 2022}
       \resumeItemListStart
            \resumeItem{Demonstrated ability to provide \textbf{24x7 on-call support}, promptly addressing ad hoc user requests.}
            \resumeItem{Extensive experience in full cycle SAP BI implementations, including requirement gathering, design and development, testing, go-live, and post-production support phases.}
            \resumeItem{Strong knowledge of front-end Business Warehouse components such as BEX Analyzer and Query Designer for creating Queries, workbooks, Calculated Key Figures, Restricted Key Figures, Structures, Variables, Exceptions.}
            \resumeItem{Strong \textbf{communication} and \textbf{mentoring skills}, providing training and knowledge transfer to new hires, ensuring a smooth onboarding process and team collaboration.}
            \resumeItem{Expertise in \textbf{ABAP} programming for writing User exits using MOD, start routine, end routine, expert routine, and info object routines related to BW.}
       \resumeItemListEnd
     \vspace{3pt}  
      \textit{\small{Busniness Technology Analyst, Client: \textbf{PayPal}\hfill{Jun 2019 \textbf{--} May 2022}}}
        \resumeItemListStart
            \resumeItem{Worked as a \textbf{Business Technology Analyst} in the \textbf{SAP BW Module}. Demonstrated ability to analyze business requirements, propose efficient solutions, and implement best practices for SAP BW and ABAP development.}
            \resumeItem{Continuous \textbf{Job monitoring} using BW Monitor. Fixing the failure and reporting data issue. Handling tickets which involve solving issues in the area of Data Extraction from R/3 and flat file, Data staging.}
            \resumeItem{Performing housing keeping activities to reduce the size of database.}
            \resumeItem{Skilled in identifying objects for migration during SAP BW 7.5 upgrade, ensuring a smooth transition and compatibility with the latest version.}
        \resumeItemListEnd
        \vspace{2pt}
    \resumeSubheading
      {Cybage Softwares Pvt. Ltd.}{Hyderabad, India}
      {Software Engineer, Client: \textbf{Pegasus}}{Nov 2018 \textbf{--} May 2019}
        \resumeItemListStart
            \resumeItem{Successfully embarked on a professional journey at Pegasus as a fresh software engineering graduate, gaining valuable hands-on experience in full stack development.}
            \resumeItem{Acquired comprehensive proficiency in key technologies, including \textbf{JAVA}, JAVA Spring MVC, \textbf{JavaScript, and Angular JS}, through dedicated training programs.}
            \resumeItem{Demonstrated exceptional organizational skills by formulating and implementing a robust QA plan, encompassing Functional, Regression, Integration, Systems, and \textbf{UAT testing}.}
            \resumeItem{Played a vital role in ensuring the delivery of high quality software by conducting rigorous testing procedures and effectively identifying and resolving issues.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Technical Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Programming:}{ SAP ABAP - OOP, Java, SQL, JavaScript, Lisp Clojure, Python, HTML, CSS, PHP} \\ \vspace{2pt}

        \textbf{SAP Technologies:}{ SAP BW, SAP BOBJ, SAP HANA} \\ \vspace{2pt}
        
        \textbf{Developer Tools:}{ Git, SAP GUI, Eclipse IDE, VS Code, Bex Analyzer, Bex Designer, Analysis for Office, Excel } \\ \vspace{2pt}
        
        \textbf{Bug Reporting Tools:}{ JIRA, ITSM, ServiceNow} \\ \vspace{2pt}

        \textbf{Databases:}{ HANA, MySQL, SQLite} \\ \vspace{2pt}

        \textbf {Strong knowledge of Object Oriented Programming and have excellent Problem-solving skills.}
        
    }}
  \resumeSubHeadingListEnd

%----------- AWARDS -----------

\section{Awards}
 \vspace{2pt}
 \resumeSubHeadingListStart
    \small{\item{
        \textbf{Applause Award from Deloitte} {I received an applause award for identifying functional issues/requirement gap beyond design document and displaying good hold on the subject area. I was very effective in driving technical discussions around the assigned user stories in the client facing scrum calls and raising potential risks/dependencies ahead of time ensuring smooth delivery}
    
    }}
  
 \resumeSubHeadingListEnd
\end{document}
